% Acknowledgements

\pdfbookmark[1]{Acknowledgements}{Acknowledgements} % Bookmark name visible in a PDF viewer

%\begin{flushright}{\slshape    
%We have seen that computer programming is an art, \\ 
%because it applies accumulated knowledge to the world, \\ 
%because it requires skill and ingenuity, and especially \\
%because it produces objects of beauty.} \\ \medskip
%--- \defcitealias{knuth:1974}{Donald E. Knuth}\citetalias{knuth:1974} \citep{knuth:1974}
%\end{flushright}

\bigskip

%----------------------------------------------------------------------------------------

\begingroup

\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax

\chapter*{Acknowledgements} % Acknowledgements section text

I wish to thank the staff and faculty of the Institute of Computational Linguistics at the University of Heidelberg for being a stimulating learning environment, for putting me on the path of natural language processing, and for endowing me with the knowledge to further pursue this path. I wish to thank my fellow undergraduate students who have accompanied me on this path; I particularly want to express my gratitude to Julius Steen and Devon Fritz for their help in the annotation task.

I particularly would like to thank my supervisor Prof. Dr. Anette Frank for her guidance, her limitless patience in light of my ceaseless requests for references, her flexibility in communicating during my semester abroad, and her good advise. I wish to thank Dr. Alexis Palmer, whose comments introduced coherence to my ramblings. I also wish to thank Dr. Michael Herweg for his conversations and seminars that have shaped my interests. 

I wish to thank Dr. Carl Vogel of Trinity College, Dublin for his guidance and advise during my semester abroad. I also want to thank my colleagues in the Linguistic Engineering Team at Microsoft, James Cogley and Declan Groves, for their guidance during my internship and their help with annotation.

Finally, I wish to thank my family, my friends, and particularly my girlfriend Jessica for their endurance and patience. I wish to dedicate this thesis to the memory of my mother and wish to thank her for making me who I am.

\endgroup